### 2022-10-17 chapters/conclusion.tex
add : drafts

>>>>

we urge energy-efficiency benchmark developers to report measurements at nonpeak activity levels for a more complete characterization of a system's energy behavior\cite{barroso2007case}.

\subsubsection*{greenFaas}
servers operate most of the time at between 10 and 50 percent of their maximum utilization levels \cite{barroso2007case}
